\beginsong{Always Look on the Bright Side of Life}[
    wuw={Monthy Pyton}, 
	jahr={1979}
    pfii={251}, 
    pfiii={131}, 
    kssiv={162}, 
    index={Some things in life are bad},
]

\transpose{-5}

\beginverse
Some \[Dm]things in life are \[Gdim7]bad, they can \[C]really make you \[Am]mad,
\[Dm]other things just \[Gdim7]make you swear and cu\[C]rse. \[C6]
When you're \[Am]chewing on life's \[Gdim7]gristle: don't \[C]grumble, give a \[Am]whistle
and \[Dm]this'll help things \[D7]turn out for the \[G]best. \[G7] And
\endverse

\beginchorus
\[C]Always \[Am]look on the \[F]bright \[G]side of life! \[C] \[Am] \[F] \[G]
\[C]Always \[Am]look on the \[F]light \[G]side of life! \[C] \[Am] \[F] \[G]
\endchorus

\beginverse\memorize
If \[Dm]life seems jolly \[G7]rotten, there's \[C]something you've for\[Am7]gotten
and \[Dm]that's to laugh and \[G7]smile and dance and \[C]sing. \[C6]
When you're \[Dm]feeling in the \[G7]dupms, \[C]don't be silly \[A7]chumps
just \[Dm]put your lips and \[D7]whistle - that's the \[G]thing! \[G7] And
\endverse

\beginchorus
\[C]Always \[Am]look on the \[F]bright \[G]side of life! \[C] \[Am] \[F] \[G]
\[C]Always \[Am]look on the \[F]right \[G]side of life! \[C] \[Am] \[F] \[G]
\endchorus

\beginverse
For ^life is quite ab^surd and ^death's the final ^word,
you must ^always face the ^curtain with a ^bow. ^
For^get about your ^sin, give the ^audience a ^grin.
En^joy it, it's your ^last chance any^how. ^
\endverse

\beginchorus 
So \[C]Always \[Am]look on the \[F]bright \[G]side of death! \[C] \[Am] \[F] \[G]
\[C]Just bef\[Am]ore you \[F]draw your \[G]terminal \[C]breath. \[Am] \[F] \[G]
\endchorus

\beginverse
^Life's a piece of ^shit, ^when you look on ^it,
^life's a laugh and ^death's a joke, it's ^true. ^
You'll ^see it's all a ^show, keep 'em ^laughing as you ^go,
just re^member that the ^last laugh is on ^you. ^
\endverse

\beginchorus
\[C]Always \[Am]look on the \[F]bright \[G]side of life! \[C] \[Am] \[F] \[G]
\[C]Always \[Am]look on the \[F]right \[G]side of life! \[C] \[Am] \[F] \[G]
\[D]Always \[Hm]look on the \[G]bright \[A]side of life! \[D] \[Hm] \[G] \[A] \rep{4}
\[D]
\endchorus

\endsong
