\beginsong{Don't Stop Believin'}[
    wuw={Journey}, 
    alb={Escape}, 
    jahr={1981}, 
    index={Just a small town girl},
    capo={4},
]

\beginverse*
\nolyrics{\[C] \[G] \[Am] \[F] \[C] \[G] \[Em] \[F]}
\endverse

\beginverse\memorize
\[C] Just a \[G]small town girl,\[Am] livin' in a \[F]lonely world.
\[C] She took the \[G]midnight train goin' \[Em]anywh\[F]ere.
\[C] Just a \[G]city boy,\[Am] born and raised in \[F]south Detroit.
\[C] He took the \[G]midnight train goin' \[Em]anywh\[F]ere.
\endverse

\beginverse*
\nolyrics{\[C] \[G] \[Am] \[F] \[C] \[G] \[Em] \[F]}
\endverse

\beginverse
\[C] A singer in a \[G]smokey room,\[Am] a smell of wine and \[F]cheap perfume.
\[C] For a smile they can \[G]share the night. It goes \[Em]on and on and \[F]on and on.
\endverse

\beginchorus
\[F]Strangers waiting,\[C] up and down the boulevard.
Their \[F]shadows searching in the \[C]night.
\[F]Streetlight people,\[C] living just to find emotion.
\[F]Hiding, somewhere in the \[G]nig\[C]ht. \[G] \[C-F]
\endchorus

\interlude{\[C] \[G] \[Am] \[F]}

\newpage

\beginverse
^ Working hard to ^get my fill,^ everybody ^want's a thrill.
^ Payin' anything to ^roll the dice, just ^one more ^time.
^ Some will win,^ some will lose.^ Some are born to ^sing the blues.
^ Oh, the movie ^never ends, it goes ^on and on and ^on and on.
\endverse

\beginchorus
\[F]Strangers waiting,\[C] up and down the boulevard.
Their \[F]shadows searching in the \[C]night.
\[F]Streetlight people,\[C] living just to find emotion.
\[F]Hiding, somewhere in the \[G]nig\[C]ht. \[G] \[C-F]
\endchorus

\interlude{\[C] \[G] \[Am] \[F] \[C] \[G] \[Em] \[F]}

\renewcommand{\everychorus}{\textnote{}}
\beginchorus
\lrep \[C]Don't stop be\[G]lievin',\[Am] hold on to that \[F]feelin',
\[C]streetlight \[G]people, oh-\[Em]oh. \[F]\rrep
\[C]Don't stop be\[G]lievin'. \[C]
\endchorus

\endsong
