\beginsong{Eve Of Destruction}[
    wuw={Barry McGuire},
    jahr={1965},
    index={The Eastern world, it is explodin'},
]

\beginverse*
{\nolyrics\[D] \[Dsus4-Dsus2] \rep{4}}
\endverse

\beginverse\memorize
The \[D]Eastern world,\[G] it is ex\[A7]plodin',
\[D] violence flarin',\[G] bullets loa\[A7]din'.
You're \[D]old enough to kill\[G] but not for \[A7]votin'.
You \[D]don't believe in war, but \[G]what's that gun you're \[A7]totin'?
And \[D]even the Jordan river has\[G] bodies fl\[A7]oatin', but you
\endverse

\beginchorus
\[D] Tell me ov\[G]er and ov\[A7]er and ov\[D]er again, my fr\[Hm]iend,
ah, you \[G]don't believe we're \[A7]on the eve of des\[D]truction. \[G] \[A7]
\endchorus

\beginverse
^Don't you understand what I'm^ tryin' to ^say?
^Can't you feel the fears I'm^ feelin' to^day?
If the ^button is pushed, there's ^no runnin' aw^ay.
There'll be ^no one to save with the ^world in a gr^ave.
Take a ^look around you boy, it's ^bound to scare you, ^boy, and you
\endverse

\printchorus

\beginverse
Yeah, my ^blood's so mad, feels ^like coagu^latin',
I'm ^sitting here just^ contem^platin'.
^I can't twist the truth, it ^knows no regu^lation.
^Handful of senators don't ^pass legis^lation,
and ^marches alone can't ^bring inte^gration,
when \[D]human respect is \[G]disinte\[A7]grating.
This \[D]whole crazy world is \[G]just too fru\[A7]strating, and you
\endverse

\printchorus

\beginverse
And ^think of all the hate there ^is in Red ^China.
Then ^take a look around to ^Selma, Ala^bama.
Ah, ^you may leave here for ^four days in ^space,
but ^when you return, it's the ^same old ^place.
The ^poundin' of the drums, the ^pride and dis^grace.
You can \[D]bury your dead, but \[G]don't leave a tr\[A7]ace.
Hate your \[D]next door neighbor but \[G]don't forget to \[A7]say grace, and
\endverse

\beginchorus
\[D] Tell me \[G]over and ov\[A7]er and ov\[D]er and over ag\[Hm]ain, my friend
you \[G]don't believe we're \[A7]on the eve of de\[D]struction.
No no, you \[G]don't believe we're \[A7]on the eve of de\[D]struction. \[G] \[D]
\endchorus

\endsong
