\beginsong{Hurt}[
    wuw={Nine Inch Nails},
    mel={Johnny Cash (Acoustic Version)} 
    alb={The Downward Spiral}, 
    jahr={1994}, 
    index={I hurt myself today}, 
    kssiv={257},
]

\beginverse*
\nolyrics{\[Am] \[\_] \[C] \[D] \[Am] \[\_] \[C] \[D]}
\endverse

\beginverse\memorize
\[Am] I \[C]hurt my\[D]self to\[Am]day, to \[C]see if \[D]I still \[Am]feel.
I \[C]focus\[D] on the \[Am]pain, the \[C]only \[D]thing that's \[Am]real.
The \[C]needle \[D]tears a \[Am]hole, the \[C]old fam\[D]iliar \[Am]sting,
try to \[C]kill it\[D] all aw\[Am]ay, but I re\[C]member \[D]everything. \[G]
\endverse

\beginchorus
\[Am]What have I be\[F]come,\[C] my sweetest \[G]friend?
\[Am]Everyone I \[F]know goes aw\[C]ay in the \[G]end.
And \[Am]you could have it \[F]all, \[G]my empire of dirt.
\[Am]I will let you \[F]down \[G]I will make you \[Am]hurt.
\endchorus

\beginverse*
\nolyrics{\[(Am)] \[\_] \[C] \[D] \[Am] \[\_] \[C] \[D]}
\endverse

\beginverse
^ I ^wear this ^crown of ^thorns up^on my ^liar's ^chair. 
^Full of ^broken ^thoughts ^I can^not re^pair. 
Be^neath the ^stains of ^time the ^feelings^ disap^pear. 
^You are ^someone ^else. ^I am ^still right \[G]here.
\endverse

\beginchorus
\[Am]What have I be\[F]come,\[C] my sweetest \[G]friend?
\[Am]Everyone I \[F]know goes aw\[C]ay in the \[G]end.
And \[Am]you could have it \[F]all, \[G]my empire of dirt.
\[Am]I will let you \[F]down \[G]I will make you \[Am]hurt.

If \[Am]I could start ag\[F]ain, a \[G]million miles away,
\[Am]I would keep my\[F]self. \[G]I would find a way.
\endchorus

\endsong
