\beginsong{Lady in Black}[
    wuw={Uriah Heep}, 
    alb={Salisbury}, 
    jahr={1971}, 
    pfii={200}, 
    pfiii={104}, 
    kssiv={198}, 
    index={She came to me one morning},
]

\transpose{+5}

\beginverse
She \[Em]came to me one morning, one lonely Sunday morning,
her \[D]long hair flowing in the \[Em]mid-winter wind.
And I \[Em]know not how she found me, for in darkness I was walking,
and de\[D]struction lay around me from a \[Em]fight I could not win.
\endverse

\beginchorus
\[Em]Ahhhhhh\[D]hhh\[Em]hhh, ahhh\[D]hhh\[Em]hhh.
\endchorus

\beginverse
She ^asked me, ''Name my foe then''. I said, ''The need within some men
to ^fight and kill their brothers without ^thought of love or God.''
And I ^begged her ''Give me horses to trample down my enemy,
so ^eager was this passion to de^vour this waste of life.
\endverse

\beginchorus
\[Em]Ahhhhhh\[D]hhh\[Em]hhh, ahhh\[D]hhh\[Em]hhh.
\endchorus

\beginverse
But she ^would not think of battles that reduces men to animals,
so ^easy to begin and yet im^possible to end.
For ^she the mother of all men had counciled me so wisely then
I ^feared to walk alone again and ^asked if she would stay.
\endverse

\beginchorus
\[Em]Ahhhhhh\[D]hhh\[Em]hhh, ahhh\[D]hhh\[Em]hhh.
\endchorus

\beginverse
''Oh ^lady lend your hand outright, oh let me rest here at your side.''
''Have ^faith and trust in me,'' she said and ^filled my heart with life.
There ^is no strength in numbers, have no such misconceptions.
But ^when you need me be assured I ^won't be far away.
\endverse

\beginchorus
\[Em]Ahhhhhh\[D]hhh\[Em]hhh, ahhh\[D]hhh\[Em]hhh.
\endchorus

\beginverse
Thus ^havin' spoke she turned away and though I found no words to say
I ^stood and watched until I saw her ^black cloak disappear.
My ^labor is no easier, but now I know I'm not alone.
I ^find new heart each time I think u^pon that windy day.
So \[Em]if one day she comes to you drink deeply from her words so wise.
Seek \[D]courage from her as your prize and \[Em]say hello for me.
\endverse

\beginchorus
\lrep \[Em]Ahhhhhh\[D]hhh\[Em]hhh, ahhh\[D]hhh\[Em]hhh.\rrep
\endchorus

\endsong
