\beginsong{Losing My Religion}[
    wuw={R.E.M.},
    jahr={1991},
    index={Oh, life is bigger},
]

\beginverse*
{\nolyrics\[F] \[G] \[Am] \[F] \[G] \[Am] \[G]}
\endverse

\beginverse\memorize
Oh \[Am]life is bigger, \[Em] it's bigger than you,
and you are \[Am]not me, the lengths that I will \[Em]go to,
the distance in your \[Am]eyes.
\[Em] Oh no I've said too \[Dm]much, I set it \[G]up.
\endverse

\beginverse
That's me in the cor^ner, that's me in the sp^otlight,
losing my reli^gion, trying to ^keep up with you,
and I ^don't know if I can do it.
^ Oh no I've said too ^much, I haven't said e^nough.
\endverse

\beginchorus
I thought that I heard you lau\[F]ghing.
I thought that I \[G]heard you \[Am]sing.
I \[F]think I thought I saw \[G]you try.\[Am] \[G]
\endchorus 

\beginverse
Every whi^sper, of every waking ^hour,
I'm choosing my con^fessions, trying to ^keep an eye on you,
like a ^hurt, lost and blinded fool, fool.
^ Oh no I've said too ^much, I set it ^up.
\endverse

\beginverse
Consider ^this, consider this the ^hint of the century,
consider ^this the slip that ^brought me to my knees, failed.
^What if all these fantasies come^ flailing around.
Now I've ^said too much.^
\endverse

\beginchorus
I thought that I heard you lau\[F]ghing.
I thought that I \[G]heard you \[Am]sing.
I \[F]think I thought I saw \[G]you try.\[Am] \[G]
\endchorus

\beginverse*
\nolyrics\[Am] \[G] \[F] \[G]
But \[C]that was just a dr\[F]eam, \[C]that was just a dr\[Dm]eam.
\endverse

\beginverse
That's me in the cor^ner, that's me in the sp^otlight,
losing my reli^gion, trying to ^keep up with you,
and I ^don't know if I can do it.
^ Oh no I've said too ^much, I haven't said e^nough.
\endverse

\printchorus

\beginverse*
But \[F]that was just a dream,\[G] \[Am]try, cry, why try?
\[F]That was just a dream, \[G]just a dr\[Am]eam, just a dr\[G]eam, dream.\[Am]
\endverse

\endsong
