\beginsong{Rolling In The Deep}[
    wuw={Adele, Paul Epworth}, 
    alb={21}, 
    jahr={2010}, 
    index={There's a fire starting},
]

\beginverse
\[Am]There's a fire start\[Em]ing in my heart,
Rea\[G]ching a fever pitch, and it's bring\[Em]ing me out the dark.\[G]
\[Am]Finally, I can see \[Em]you crystal clear.
Go \[G]ahead and sell me out, and I'll \[Em]lay your ship bare.\[G]
\endverse

\beginverse
^See how I'll leave with eve^ry piece of you,
don't un^derestimate the things ^that I will do.^
^There's a fire start^ing in my heart,
reach^ing a fever pitch, and it's bring^ing me out the dark.^
\endverse

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[F] The scars of \[G]your love, remind me \[Em]of us,
they keep me \[F]thinking that we almost \[G]had it \[F]all.
The scars of \[G]your love, they leave me \[Em]breathless,
I can't help \[E7]feeling...
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Refrain 1}}
\beginchorus
We could have had it \[Am]a\[G]ll, \hfill\echo{\[(Am)]You're gonna wish you, \[(G)]never had met me,}
Rolling in the \[F]Deep. \hfill\echo{\[(F)]tears are gonna fall, rolling in the \[(G)]deep.}
You \[G]had my heart in\[Am]side of your \[G]hand, \hfill\echo{\[(Am)]You're gonna wish you, \[(G)]never had met me,}
and you \[F]played it to the beat. \[G] \hfill\echo{\[(F)]tears are gonna fall, rolling in the \[(G)]deep.}
\endchorus

\beginverse
^Baby I have no sto^ry to be told,
But I've ^heard one on you, now I'm gonna ^make your head burn^
^Think of me in the depths ^of your despair,
make ^a home down there, as mine ^sure won't be shared.^
\endverse

\renewcommand{\everychorus}{\textnote{\bf Bridge and Refrain 1}}
\beginchorus\endchorus

\renewcommand{\everychorus}{\textnote{\bf Refrain 2}}
\beginchorus
Could have had it \[F]a\[G]ll, Rolling in the \[Am]De\[G]ep.
You had my heart in\[F]side of your hand, but you pl\[G]ayed it with a beating.
\endchorus

\beginverse
\[Am]Throw yourself through every open door. \echo{W\[Em]hoa}
\[Am]Count your blessings to find what you look for. \echo{W\[Em]hoa}
\[Am]Turn my sorrow into treasured gold. \echo{W\[Em]hoa}
You'll \[Am]pay me back in kind and reap just what you sow.\[G]
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain 3}}
\beginchorus
\[Am] ~~~~~~~~~~~~ \[G]  ~\hfill\echo{\[(Am)]You're gonna wish you, \[(G)]never had met me,}
We could have had it \[F]all, \hfill\echo{\[(F)]tears are gonna fall, rolling in the \[(G)]deep.}
We \[G]could have had it \[Am]all, \[G] \hfill\echo{\[(Am)]You're gonna wish you, \[(G)]never had met me,}
it \[F]all, it all, it all...\[G] \hfill\echo{\[(F)]tears are gonna fall, rolling in the \[(G)]deep.}
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Refrain 1 (x2)}}
\beginchorus
But you \[F]played it, you played it, you played it, you pla\[G]yed it to the \[Am]beat.
\endchorus

\endsong
