\beginsong{Space Oddity}[
    wuw={David Bowie}, 
    alb={David Bowie}, 
    jahr={1969}, 
    index={Ground Control to Major Tom},
]


\begin{minipage}{.85\textwidth}%
\interlude{\lrep \[Fmaj7] \[Em] \[Fmaj7] \[Em] \rrep}

\beginverse
\[C] Ground Control to Major \[Em]Tom,
\[C] Ground Control to Major \[Em]Tom,
\[Am] take your \[Am7/G]protein pills and \[D7/F#]put your helmet on.
\[C] Ground control to Major \[Em]Tom. \hfill\echo{\[(C)]ten, nine, \[(Em)]eight, seven}
\[C] Commencing countdown, engines \[Em]on. \hfill\echo{\[(C)]six, five, \[(Em)]four, three}
\[Am] Check ign\[Am7/G]ition and may \hfill\echo{\[(Am)]two, \[(Am7/G)]one}
\[D7/F#]God's love be with you! \hfill\echo{\[(D7/F#)]liftoff}
\endverse
\end{minipage}%
\begin{minipage}{.15\textwidth}
    \vspace{0pt}
    \begin{flushright}
        \hfill\gtab{Fmaj7}{X33210}
        \hfill\gtab{Am7/G}{332010}
        \hfill\gtab{D7/F#}{200212}
        \hfill\gtab{Em7}{055430}
    \end{flushright}
\end{minipage}%

\newchords{space_oddity_chorus}
\beginchorus\memorize[space_oddity_chorus]
\[C]This is Ground Control to Major \[E7]Tom, you've really made the \[F]grade!
And the \[Fm]papers want to \[C]know whose shirts you \[F]wear,
now it's \[Fm]time to leave the \[C]capsule if you \[F]dare.
\[C]This is Major Tom to Ground Con\[E7]trol, I'm stepping through the \[F]door.
And I'm \[Fm]floating in a \[C]most peculiar \[F]way,
and the \[Fm]stars look very \[C]different to\[F]day.
\endchorus

\newchords{space_oddity_bridge}
\beginverse*\memorize[space_oddity_bridge]
For \[Fmaj7]here am I \[Em7]sitting in a tin can, \[Fmaj7]far above the \[Em7]world, 
\[B]Planet Earth is \[Am]blue, and there's \[G]nothing I can \[F]do.
\begin{nolyrics}
\lrep \[C] \[F] \[G] *cl\[A]ap* *cl\[A]ap* \rrep
\[Fmaj7] \[Em7] \[A] \[C] \[D7] \[E]
\end{nolyrics}
\endverse


\beginchorus\replay[space_oddity_chorus]
^Though I'm past one hundred thousand ^miles, I'm feeling very ^still,
and I ^think my spaceship ^knows which way to ^go.
Tell my ^wife I love her ^very much she ^knows.
\[G]Ground Control to \[E7]Major Tom, Your \[Am]circuit's dead, there's \[Am7]something wrong.
Can you \[D]hear me, Major Tom?
Can you \[C]hear me, Major Tom?
Can you \[G]hear me, Major Tom?
Can you-
\endchorus

\beginverse*\replay[space_oddity_bridge]
^Here am I ^floating 'round my tin can, ^far above the ^moon,
^Planet Earth is ^blue, and there's ^nothing I can ^do.
\begin{nolyrics}
\lrep ^ ^ ^ *cl^ap* *cl^ap* \rrep
^ ^ ^ ^ ^ ^
\[Fmaj7] \[Em7] \[Fmaj7] \[Em7] \[Fmaj7] \[Em7] \[Aadd9]
\end{nolyrics}
\endverse

\endsong