\beginsong{The Sound of Silence}[
    wuw={Simon \& Garfunkel},
    jahr={1964},
    index={Hello darkness, my old friend},
    capo={6}
]

\beginverse\memorize
\[Am] Hello darkness, my old \[G]friend,
I've come to talk with you a\[Am]gain.
Because a \[C]vision soft\[F]ly creep\[C]ing,
Left its seeds while I wa\[F]s sleep\[C]ing,
And the \[F]vision that was planted in my br\[C]ain
Still remains \[Am] \[C]
Within the \[G]sound of \[Am]silence.
\endverse

\beginverse
^ In restless dreams I walked a^lone,
Narrow streets of cobble^stone.
'Neath the ^halo of a^ street la^mp,
I turned my collar to the ^cold and da^mp.
When my ^eyes were stabbed by the flash of a neon li^ght
That split the night, ^ ^
And touched the ^sound of ^silence.
\endverse

\beginverse
^ And in the naked light I ^saw
Ten thousand people, maybe ^more.
People ^talking with^out speak^ing.
People hearing with^out listen^ing.
People writing ^songs that voices never sh^are.
No one dared ^ ^
Disturb the ^sound of ^silence.
\endverse

\beginverse
^ ''Fools'' said I, ''You do not ^know,
Silence like a cancer ^grows.
Hear my ^words that I mi^ght teach y^ou,
Take my arms that I mi^ght reach y^ou.''
But my ^words like silent raindrops ^fell, ^
And ^echoed in the ^wells of ^silence.
\endverse

\beginverse
^ And the people bowed and ^prayed,
To the neon god they ^made.
And the ^sign flashed out i^ts warn^ing,
In the words that it wa^s form^ing.
And the sign said, ''The ^words of the prophets are written on the subway wal^ls
And tenement halls.'' ^
And ^whispered in the ^sounds of ^silence.
\endverse

\endsong
