\beginsong{Under the Bridge}[
    wuw={Red Hot Chili Peppers}, 
    alb={Blood Sugar Sex Magik}, 
    jahr={1991}, 
    pfiii={82}, 
    index={Sometimes I feel like I don't have a partner},
]

\begin{minipage}{.85\textwidth}%
\beginverse*
{\nolyrics \[D] \[F\#] \[D] \[(E)] \[F\#] \rep{2}}
\endverse 

\beginverse\memorize
\[E] Sometimes \[H]I feel like I \[C\#m]don't have a \[G\#m]part\[A]ner,
\[E] sometimes \[H]I feel like \[C\#m]my only \[A]friend.
Is the \[E]city I \[H]live in, the \[C\#m]city of \[G\#m]an\[A]gels?
\[E]Lonely as \[H]I am, to\[C\#m]gether we \[A]cry. \[Emaj7]
\endverse

\beginverse
I ^drive on her ^streets 'cause ^she's my com^pan^ion,
I ^walk through her ^hills 'cause she ^knows who I ^am. 
She ^sees my good ^deeds and she ^kisses me ^win^dy,
^I never ^worry, now ^that is a ^lie. ^
\endverse
\end{minipage}%
\begin{minipage}{.15\textwidth}
    \vspace{0pt}
    \begin{flushright}
        \hfill\gtab{Am7/C}{X32010}
        \hfill\gtab{G6}{320000}
        \hfill\gtab{Fmaj7/A}{X03210}
        \hfill\gtab{Fmaj7}{X33210}
    \end{flushright}
\end{minipage}%

\beginchorus
\[F\#m]I don't ever want \[E]to feel\[H] like \[F\#m]I did that day,
take me to the place \[E]I love,\[H] take \[F\#m]me all the way.
I don't ever want \[E]to feel\[H] like \[F\#m]I did that day,
take me to the place \[E]I love,\[H] take \[F\#m]me all the way,\[E] \[H]yeah, \[C\#m]yeah, \[G\#m]ye\[A]ah.
\endchorus

\interlude{\[E] \[H] \[C\#m] \[A]}

\beginverse
It's ^hard to be^lieve that there's ^nobody ^out ^there,
it's ^hard to be^lieve, that ^I'm all a^lone.
At ^least I have ^her love, the ^city she ^loves ^me,
^lonely as ^I am, to^gether we ^cry. ^
\endverse

\beginchorus
\[F\#m]I don't ever want \[E]to feel\[H] like \[F\#m]I did that day,
take me to the place \[E]I love,\[H] take \[F\#m]me all the way.
I don't ever want \[E]to feel\[H] like \[F\#m]I did that day,
take me to the place \[E]I love,\[H] take \[F\#m]me all the way, \newline
\[A] \[Am7/C]yeah, \[G6]yeah, \[Fmaj7/A]yeah.
\[A]Oh, \[Am7/C]no, nono, \[G6]yeah, \[Fmaj7/A]yeah.
\[A]Love \[Am7/C]me, I say, \[G6]Yeah, \[Fmaj7/A]yeah. \[Fmaj7] \[E] \[G] \newline

\echo{\[A]Under the bridge \[Am7/C]downtown...}\[G6] is where \[Fmaj7/A]I drew some blood.
\echo{\[A]Under the bridge \[Am7/C]downtown...}\[G6] I could \[Fmaj7/A]not get enough.
\echo{\[A]Under the bridge \[Am7/C]downtown...}\[G6] forgot \[Fmaj7/A]about my love.
\echo{\[A]Under the bridge \[Am7/C]downtown...}\[G6] I gave \[Fmaj7/A]my life away, \newline
\[A] \[Am7/C]yeah, \[G6]yeah, \[Fmaj7/A]yeah.
\[A]Oh, \[Am7/C]no, nono, \[G6]yeah, \[Fmaj7/A]yeah. \echo{Away}
\[A]No, \[Am7/C]no, I say, \[G6]yeah, \[Fmaj7/A]yeah. \echo{Away}
\[A] \[Am7/C] Here I stay.\[G6] \[Fmaj7/A] \echo{Away}
{\nolyrics \[A] \[Am7/C] \[G6] \[Fmaj7/A] \rep{4} \[A]}
\endchorus

\endsong
