\beginsong{We are the Champions}[
    wuw={Queen},  
    alb={News of the World}, 
    jahr={1977}, 
    pfi={17}, 
    pfii={259}, 
    pfiii={134}, 
    index={I've paid my dues}, 
    capo={3},
]

\beginverse
I've paid my \[Am]dues\[Em], time after \[Am]time\[Em].
I've done my \[Am]sentence\[Em], but committed no \[Am]crime\[Em].
And bad mis\[C]takes\[F], I've made a \[C]few\[F],
I've had my \[C]share of sand \[G]kicked in my \[Am]face,
but \[D7]I've come \[G]through. \echo{and I mean to go on, and on, and \[G7]on, and \[A]on}
\endverse

\beginchorus
\[D]We are the \[F\#m]champions, my \[Hm]friend. \[G] \[A]
And \[D]we'll keep on \[F\#m]fighting till the \[G]end. \[H7]
\[Em]We are the \[A7]champions, \[Gm]we are the champions.
\[D]No time for \[C]losers, 'cause \[F]we are the \[G]champions! \[Am7add4]
... of the \[Dm]world. \[Em7] \[Dm] \[Em7] \[Dm] \[Em7/A]
\endchorus

\beginverse
I've taken my ^bows^, and my curtain ^calls^.
You brought me ^fame and fortune and everything that 
^goes with it, I thank you ^all. ^
But it's been no bed of ^roses^, no pleasure ^cruise^,
I consider it a ^challenge before ^the whole human ^race,
and ^I ain't gonna l^ose. \echo{and I mean to go on, and on, and ^on, and ^on}
\endverse

\beginchorus
\[D]We are the \[F\#m]champions, my \[Hm]friend. \[G] \[A]
And \[D]we'll keep on \[F\#m]fighting till the \[G]end. \[H7]
\[Em]We are the \[A7]champions, \[Gm]we are the champions.
\[D]No time for \[C]losers, 'cause \[F]we are the \[G]champions\[Am7add4] of the-
\[D]We are the \[F\#m]champions, my \[Hm]friend. \[G] \[A]
And \[D]we'll keep on \[F\#m]fighting till the \[G]end. \[H7]
\[Em]We are the \[A7]champions, \[Gm]we are the champions.
\[D]No time for \[C]losers, 'cause \[F]we are the \[G]champions.\[Am7add4]
\endchorus

\endsong
