\beginsong{What Shall We Do With The Drunken Sailor}[
    wuw={nach einem Arbeitslied der Seefahrer}, 
    pfii={209}, 
    pfiii={111}, 
    kssiv={65}, 
    siru={278},
]

\beginverse
\[Dm]What shall we do with the drunken sailor? \[C]What shall we do with the drunken sailor?
\[Dm]What shall we do with the drunken sailor? \[C]Early in the \[Dm]morning?
\endverse

\beginchorus
\[Dm]Hoo-ray, and up she rises, \[C]Hoo-ray, and up she rises
\[Dm]Hoo-ray, and up she rises, \[C]Early in the \[Dm]morning.
\endchorus

\beginverse
^Take him and shake him and try to awake him. ^Take him and shake him and try to awake him.
^Take him and shake him and try to awake him. ^Early in the ^morning.
\endverse

\printchorus

\beginverse
^Put him in the long-boat till he's sober. ^Put him in the long-boat till he's sober.
^Put him in the long-boat till he's sober. ^Early in the ^morning.
\endverse

\printchorus

\beginverse
^Shave his belly with a rusty razor. ^Shave his belly with a rusty razor.
^Shave his belly with a rusty razor. ^Early in the ^morning.
\endverse

\printchorus

\beginverse
^Give him a dose of salt and water. ^Give him a dose of salt and water.
^Give him a dose of salt and water. ^Early in the ^morning.
\endverse

\newpage

\beginchorus
\[Dm]Hoo-ray, and up she rises, \[C]Hoo-ray, and up she rises
\[Dm]Hoo-ray, and up she rises, \[C]Early in the \[Dm]morning.
\endchorus

\beginverse
^Put him in bed with the captain's daughter. ^Put him in bed with the captain's daughter.
^Put him in bed with the captain's daughter. ^Early in the ^morning.
\endverse

\printchorus

\beginverse
^Pull out the plug and wet him all over. ^Pull out the plug and wet him all over.
^Pull out the plug and wet him all over. ^Early in the ^morning.
\endverse

\printchorus

\beginverse
^Put him in a pot of ice-cold water. ^Put him in a pot of ice-cold water.
^Put him in a pot of ice-cold water. ^Early in the ^morning.
\endverse

\printchorus

\beginverse
^That's what we do with the drunken sailor. ^That's what we do with the drunken sailor.
^That's what we do with the drunken sailor. ^Early in the ^morning.
\endverse

\printchorus

\endsong
