\beginsong{Wonderwall}[
    wuw={Oasis}, 
    alb={(What’s the Story) Morning Glory?}, 
    jahr={1995}, 
    pfiii={144}, 
    kssiv={278}, 
    siru={227}, 
    index={Today is gonna be the day},
    capo={2},
]

\begin{minipage}{.85\textwidth}%
\beginverse*
{\nolyrics \[Em7] \[G] \[Dsus4] \[A7sus4] \rep{4}}
\endverse

\beginverse\memorize
\[Em7] Today is \[G]gonna be the day
that they're \[Dsus4]gonna throw it back to \[A7sus4]you.
\[Em7] By now you \[G]should have somehow
rea\[Dsus4]lised what you gotta \[A7sus4]do.
\[Em7]I don't believe that \[G]anybody \[Dsus4]feels the way I \[A7sus4]do
About you \[Cadd9]now. \[Dsus4] \[A7sus4]
\endverse

\beginverse
^ Back beat, the ^word is on the street
that the ^fire in your heart is ^out.
^ I'm sure you've ^heard it all before,
but you ^never really had a ^doubt.
^I don't believe that ^anybody ^feels the way I ^do
About you \[Em7]now. \[G] \[Dsus4] \[A7sus4]
\endverse
\end{minipage}%
\begin{minipage}{.15\textwidth}
    \begin{flushright}
    \hfill\gtab{Em7}{022033}
    \hfill\gtab{G}{320033}
    \hfill\gtab{Dsus4}{XX0233}
    \hfill\gtab{A7sus4}{X02233}
    \hfill\gtab{Cadd9}{X32033}
    \end{flushright}
\end{minipage}%

\beginverse*
And \[Cadd9]all the roads we \[Dsus4]have to walk are \[Em7]winding,
And \[Cadd9]all the lights that \[Dsus4]lead us there are \[Em7]blinding,
\[Cadd9]There are many \[Dsus4]things that I would \[G]like to \[Dsus4/f#]say to \[Em7]you
But I \[G]don't know \[A7sus4]how.
\endverse

\beginchorus
Because \[Cadd9]maybe,\[Em7] \[G] you're \[Em7]gonna be the one that \[Cadd9]saves me,\[Em7] \[G]
And \[Em7]after \[Cadd9]all, \[Em7] \[G] you're my \[Em7]wonder\[Cadd9]wall. \[Em7] \[G] \[Em7]
\nolyrics \[A7sus4]
\endchorus

\beginverse
^ Today was ^gonna be the day,
but they'll ^never throw it back to ^you.
^ By now you ^should have somehow
Rea^lised what you're not to ^do.
^I don't believe that ^anybody ^feels the way I ^do
about you \[Em7]now. \[G] \[Dsus4] \[A7sus4]
\endverse

\beginverse*
And \[Cadd9]all the roads that \[Dsus4]lead you there are \[Em7]winding.
And \[Cadd9]all the lights that \[Dsus4]light the way are \[Em7]blinding.
\[Cadd9]There are many \[Dsus4]things that I would \[G]like to \[Dsus4/f#]say to \[Em7]you
But I \[G]don't know \[A7sus4]how.
\endverse

\repchorus{2}

\beginchorus
I said \[Cadd9]maybe, \[Em7] \[G] 
You're \[Em7]gonna be the one that \[Cadd9]saves me, \[Em7] \[G]
You're \[Em7]gonna be the one that \[Cadd9]saves me, \[Em7] \[G]
You're \[Em7]gonna be the one that \[Cadd9]saves me... \[Em7] \[G] \[Em7]
\nolyrics \[Cadd9] \[Em7] \[G] \[Em7] \rep{4}
\endchorus

\endsong
